---
title: "FishRatioR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FishRatioR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FishRatioR)
```

## 1.Example data view and usage

```{r}
data("famgenspe")

famgenspe
```

## 2. Calculate Ratio values

> **Formula**: Ratio = (N_species_in_genus) / (N_species_in_family)

```{r}
ratio <- calc_ratio(famgenspe = famgenspe)

ratio
```

## 3. Calculate Ln(Ratio) values

> **Formula**: Ln(Ratio) = Ln((N_species_in_genus) / (N_species_in_family))

```{r}
ln_ratio <- calc_ln_ratio(famgenspe = famgenspe)

ln_ratio
```

## 4. Calculate Ratio(-Ln(Ratio)) values

> **Formula**: NegMulRatio = Ratio \* (-Ln((N_species_in_genus) / (N_species_in_family)))

```{r}
mul_ratio <- calc_mul_ratio(famgenspe = famgenspe)

mul_ratio
```

## 5. Calculate all values based one step

> **Formula**: Ratio = (N_species_in_genus) / (N_species_in_family), Ln(Ratio) = Ln((N_species_in_genus) / (N_species_in_family)), NegMulRatio = Ratio \* (-Ln((N_species_in_genus) / (N_species_in_family)))

```{r}
all_ratio <- calc_all(famgenspe = famgenspe)

all_ratio
```

## 6. FishRatioR for Python

> [**FishRatio PYPI Code**](https://github.com/benben-miao/FishRatio)**: <https://github.com/benben-miao/FishRatio>**
>
> [**FishRatio PYPI**](https://pypi.org/project/fishratio)**: <https://pypi.org/project/fishratio>**

```{=html}
pip install fishratio
  
  fishratio --help
  Usage: fishratio [OPTIONS]
  
       Description:
  
       Calculate the ratio and logarithmic value of species contained in
       several genus of a family to all species in this family.
  
       Examples:
  
       1. Get options and parameters help:
  
       FishRatio --help
  
       2. Sample command with all default parameters:
  
       FishRatio --input input.xlsx     or
  
       FishRatio --input input.xlsx --ratio true --ln_ratio true --neg_ratio
       true --output output.xlsx
  
       3. Only calculate (species number of genus) / (species number of
       family):
  
       FishRatio --input input.xlsx --ratio true --ln_ratio false --neg_ratio
       false --output output.xlsx
  
  Options:
    --input TEXT        Full name (path + name + extension) of input file.
                        default="input.xlsx"
  
    --ratio BOOLEAN     Formula: (species number of genus) / (species number of
                        family) ratio value. default=True
  
    --ln_ratio BOOLEAN  Formula: Log(e)(ratio value). default=True
    --neg_mul BOOLEAN   Formula: -(ratio x Log(e)(ratio value)). default=True
    --output TEXT       Full name (path + name + extension) of output file.
                        default="output.xlsx"
  
    --help              Show this message and exit.
```
